Predicting the Quality of CDRH3 Antibody Loop Structural Models

### 2022-10-05 paper.tex
Fixed Figure references

According to the Kabat definition, the CDR-H3 loop is made up of the
residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
chain, with a potential insertion site at position 100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long \ref{fig:loopdist}.

@@

\section{Results}
To asses the predictive power regarding the CDR-H3 loop, the software
was tested on a test-set of antibody structures used in the 2014 and
2011 Antibody Modelling Assessments
\cite{Almagro2011,Almagro2014}. As the results depicted in
\ref{fig:AMA} show, abYmod achieves results similar to, or better than
other modelling programs. However, the outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work
would aim to identify such outlier models.

@@

The full pipeline for creating the final machine learning model that
will predict model quality by giving its RMSD range starts with a
feature-set calculation using the antibody sequence. The feature set
includes many different attributes linked to sequence, physical
characteristics, interactions, etc. within as well as outside of the
loop. There is a plethora of information to train our classifier on,
including packing quality, protrusion, hydrophobicity, pseudo-energy
(see protrusion, hydrophobicity, pseudo-energy (see methods for
details). The sequence logo \ref{fig:logo} visualizes amino acid
occurrence within the loop sequence, elements of which can be
extracted as features \cite{Thomsen2012,Shaner1993}.

@@

The classifier predicts whether a model has an RMSD of below 2\AA,
between 2-4\AA, or above 4\AA. These cut-off values were selected
based on the observation that abYmod generally produces a model with
RMSD below 4\AA. Incorrectly modelled structures (\ref{fig:AMA}) may
be identified by screening for structures estimated to have an RMSD
above 4\AA. If a very high-quality model is needed one should also
exclude models above 2\AA.

>>>>

According to the Kabat definition, the CDR-H3 loop is made up of the
residues 95-105 (Kabat numbering scheme\cite{Kabat1992}) in the heavy
chain, with a potential insertion site at position 100. The
possibility of such an insertion of a varying number of residues leads
to a large range of loop lengths, with bovine antibodies being
exceptionally long (Figure~\ref{fig:loopdist}).

@@

\section{Results}
To asses the predictive power regarding the CDR-H3 loop, the software
was tested on a test-set of antibody structures used in the 2014 and
2011 Antibody Modelling Assessments
\cite{Almagro2011,Almagro2014}. As the results depicted in
Figure~\ref{fig:AMA} show, abYmod achieves results similar to, or better than
other modelling programs. However, the outliers with very high RMSD
values increase abYmod's RMSD average. The predictor in this work
would aim to identify such outlier models.

@@

The full pipeline for creating the final machine learning model that
will predict model quality by giving its RMSD range starts with a
feature-set calculation using the antibody sequence. The feature set
includes many different attributes linked to sequence, physical
characteristics, interactions, etc. within as well as outside of the
loop. There is a plethora of information to train our classifier on,
including packing quality, protrusion, hydrophobicity, pseudo-energy
(see protrusion, hydrophobicity, pseudo-energy (see methods for
details). The sequence logo (Figure~\ref{fig:logo}) visualizes amino acid
occurrence within the loop sequence, elements of which can be
extracted as features \cite{Thomsen2012,Shaner1993}.

@@

The classifier predicts whether a model has an RMSD of below 2\AA,
between 2-4\AA, or above 4\AA. These cut-off values were selected
based on the observation that abYmod generally produces a model with
RMSD below 4\AA. Incorrectly modelled structures (Figure~\ref{fig:AMA}) may
be identified by screening for structures estimated to have an RMSD
above 4\AA. If a very high-quality model is needed one should also
exclude models above 2\AA.
